\title{EXOSIMS Run and Post Processing Automation}
\author{
		Dean Keithly
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{dirtree,float}
\usepackage{bibentry}

\begin{document}
\maketitle

%\begin{abstract}
%This is the paper's abstract \ldots
%\end{abstract}

\section{setupEXOSIMS.py}
setupEXOSIMS.py is designed to be run from level 1 of the EXOSIMS repository (the same folder where documentation, ICD, tests, and EXOSIMS folders exist).
This script creates the "Scripts", "cache", and "fitFilesFolder"  at level 0 (one folder level above level1, the EXOSIMS repository).
This script copies the makeSimilarScripts.py, singleRunPostProcessing.py, and multiRunPostProcessing.py scripts to the level 0 scripts folder.
The script also copies deleteMe100.json (a templeate script), makeSimilar.json, makeSimilar2.json (the makeSimilarScripts.py instruction files) to the Scripts folder which form the base examples of how to use makeSimilarScripts.py. 
This script uses setuptools.command.easy\_install to install the python modules listed in requirements.txt.


\section{Directory Tree}
\fbox{%
	\small
	
\noindent\begin{minipage}[t]{0.99\linewidth\relax}
	\dirtree{%
	.1 /exosims (Folder Where EXOSIMS module is located). 
	.2 /EXOSIMS. 
	.3 setupEXOSIMS.py. 
	.3 /tests. 
	.3 /ICD. 
	.3 /EXOSIMS. 
	.4 /run. 
	.4 /Scripts. 
	.5 TemplateScript1.json. 
	.5 TemplateScript2.json. 
	.2 /Scripts (External Scripts Folder). 
	.3 makeSimilarScripts.py. 
	.3 makeSimilarJson.py. 
	.3 queue.json. 
	.3 deleteMe100.json. 
	.3 makeSimilar.json. 
	.3 /makeSimilar\_deleteM100. 
	.4 deleteMe100.json. 
	.4 makeSimilar.json. 
	.4 queue\_*date*\_makeSimilar\_deleteMe100.json. 
	.4 *List of scripts created by deleteMe100.json and makeSimilar.json*.
	.2 /cache. 
	.3 queue.json. 
	.3 runLog.csv. 
	.3 *.comp. 
	.3 ....
	.2 /fitFilesFolder. 
	}
	\end{minipage}
}

\subsection{cache}
\subsection{Scripts}
The Scripts folder is where makeSimilarScripts.py is designed to be run from.
The Scripts folder should contain all makeSimilarInst.json files.
If makeSimilarInst.json file refers to a Template.json file as the template script, then that script should be located in the Scripts folder.
A note on operation of makeSimilarScripts.py: If a makeSimilarInst.json file refers to a Template file Template.json and this Template.json file has a field which is a file name, that file will be copied into the subfolder makeSimilarInst\_Template with 'auto\_makeSimilarInst\_Template' prepended to the filename (This ensure that all necessary information required to replicate a given run is contained within the makeSimilarInst\_Template folder).
\paragraph{Example:} If a makeSimilarInst.json file refers to a Template.json file with a "missionSchedule" dictionary key with value "sampleOB.csv", then sampleOB.csv should reside in the Scripts folder.
When makeSimilarScripts.py is run, a copy of sampleOB.csv will be made in makeSimilarInst\_Template with filename auto\_makeSimilarInst\_TemplatesampleOB.csv.
\subsection{fitFilesFolder}
The fitFilesFolder is where fit files should be stored (EXOSIMS does not require this as of 9/18/2018 and is not anticipated to require this).


%%% OLD makeSimilarScripts.py < Sept 15th 2018
\section{makeSimilarScripts.py}
This script is designed to be run from the 'EXOSIMS/../Scripts' folder.
The template script scriptAAA.json must be located in the 'EXOSIMS/../Scripts' folder.
\paragraph{Inputs:}
makeSimilarInst.json - this file is located in the run directory and encodes the instructions for making a set of similar json input scripts.
scriptAAA.json
\paragraph{Outputs:}
queueXXX.json - this file is a queue containing a list of all


\subsection{makeSimilarInst.json}
Every configuration of this script has keys
'sweepType' and 'sweepParameters'.
The 'sweepType' field must be a string.
'sweepType' has valid input fields of "SweepParameters" and "SweepParametersPercentages".
The 'sweepParameters' field must be a list of strings where each string is a valid key of the EXOSIMS json script.

\subsubsection{SweepParameters}
The 'sweepType' "SweepParameters" is designed to sweep any set of parameters in 'sweepParameters' key.
The makeSimilarInst.json must have the 'sweepValues' key.
The 'sweepValues' key must have the same length as the 'sweepParameters' key.
i.e. 'sweepParameters':[param1, param2, ..., paramn] and 'sweepValues':[vals1, vals2, ..., valsn] where the length of both lists are n
Each valsi in 'sweepValues' is a list of values.
Each list valsi in 'sweepValues' has the same length.
The number of executable EXOSIMS created has length len(valsi).

\subsubsection{SweepParametersPercentages}
The 'sweepType' "SweepParametersPercentages" is designed to take a set of parameters and set of percentages and run percentage based sweeps on single and combinations of parameters.
This 'sweepType' requires a 'sweepPercentages', 'sweepParameters', and 'sweepCombNums'.

\paragraph{The 'sweepCombNums'} are a list of sweep combination lengths (i.e. sweepCombNums = [1] means each parameter).
\paragraph{The 'sweepPercentages'} are a list of percentages   where XX\% is 0.XX and -XX\% is -0.XX. 
The list must contain at least 1 element but may contain an arbitrarily large number of elements.
No element may contain less than or equal to -100\%.
\paragraph{The 'sweepParameters'} can be any number of parameters, but all parameters will be varied by the same percentage.

%\subsubsection{SweepParametersUniquePercentages}
%The 'sweepType' "SweepParametersUniquePercentages" is designed to take a set of parameters  percentages and run percentage based sweeps on single and combinations of parameters.


\section{runQueue}
\paragraph{Inputs:}
outpath (string) - this is the full filepath to the "output directory". This "output directory" is the location that each "job" directory will be saved. A "job" is a specific json script which is executed over a number of runs (numRuns).
queue.json (file) - see \ref{sec:queue.json}
\paragraph{Outputs:}


\section{queue.json}\label{sec:queue.json}
This file is located in the "EXOSIMS/../cache" directory.
This json file encodes the "scriptNames" and "numRuns".
"scriptNames" is a list of strings where each string is a filename of a file that exists in the "EXOSIMS/../Scripts" folder.
"numRuns" is a list of integers with same length as "scriptNames" where each number of runs is the number of runs to execute for the corresponding script name.

\nocite{*}
%\bibstyle{}
\bibliographystyle{plain}
\nobibliography{main}
%\bibliography{masterthesis}
%\bibliographystyle{abbrv}
%\bibliography{main.bib}

\end{document}